tl20-05_berghei_pir_DESEQ

### 2021-10-04 chapter3_results_bergheiPir/Manuscript_berghei_pir_DESEQ.Rmd
Save stats and read in stats and print specific stats

```{r lfcShrink}
shrunk.list <- lapply(comparisons, 
                      function(comparison){
                        res <- results(
                          dds.deseq,
                          contrast = c("stage",comparison[1],comparison[2])
                        )
                        shrunk <- lfcShrink(dds.deseq, 
                                            res = res,
                                            type = "ashr") %>% 
                          as.data.frame %>% 
                          rownames_to_column(var = 'Geneid') %>% 
                          mutate(comp = paste0(comparison[1],'_',comparison[2])) %>% 
                          filter(Geneid %in% pir_geneset$pirs,
                                 !is.na(padj))
                        return(shrunk)
                      })
names(shrunk.list) <- unlist(lapply(comparisons, 
                                    function(comparison) paste0(comparison[1],'_',comparison[2])))
sig_pirs <- bind_rows(shrunk.list) %>% 
  mutate(subfam = pir_info$clade[match(Geneid, pir_info$Geneid)]) %>% 
  arrange(subfam, Geneid) %>% 
  filter(padj < 0.05)
sig_pirs_order <- unique(sig_pirs$Geneid)
sig_pirs_cast <- dcast(sig_pirs,
                       comp ~ Geneid,
                       value.var = 'log2FoldChange') %>% 
  column_to_rownames(var = 'comp')
sig_pirs_cast <- sig_pirs_cast[ordering(rownames(sig_pirs_cast),
                                        c(r_order_vector,
                                          'Gam.Male_Asex.Mixed',
                                          'Gam.Male_Liv.Meroz')),
                               sig_pirs_order]

sig_pirs %>% filter(Geneid %in% 'PBANKA_0317181')
sig_pirs %>% filter(Geneid %in% 'PBANKA_0600031')
```

@@

```{r save_stats_df}
deseq_stats <- bind_rows(shrunk.list) %>% 
  mutate(subfam = pir_info$clade[match(Geneid, pir_info$Geneid)]) %>% 
  arrange(subfam, Geneid)

write_xlsx(deseq_stats, 
           'SupplementaryInformation4_Stats_DESEQ_berghei.xlsx')
write.csv(deseq_stats, 
           'SupplementaryInformation4_Stats_DESEQ_berghei.csv')

>>>>

```{r lfcShrink}
shrunk.list <- lapply(comparisons, 
                      function(comparison){
                        res <- results(
                          dds.deseq,
                          contrast = c("stage",comparison[1],comparison[2])
                        )
                        shrunk <- lfcShrink(dds.deseq, 
                                            res = res,
                                            type = "ashr") %>% 
                          as.data.frame %>% 
                          rownames_to_column(var = 'Geneid') %>% 
                          mutate(comp = paste0(comparison[1],'_',comparison[2])) %>% 
                          filter(Geneid %in% pir_geneset$pirs,
                                 !is.na(padj))
                        return(shrunk)
                      })
names(shrunk.list) <- unlist(lapply(comparisons, 
                                    function(comparison) paste0(comparison[1],'_',comparison[2])))

deseq_stats <- bind_rows(shrunk.list) %>% 
  mutate(subfam = pir_info$clade[match(Geneid, pir_info$Geneid)]) %>% 
  arrange(subfam, Geneid)

sig_pirs <- filter(deseq_stats, padj < 0.05)
sig_pirs_order <- unique(sig_pirs$Geneid)
sig_pirs_cast <- dcast(sig_pirs,
                       comp ~ Geneid,
                       value.var = 'log2FoldChange') %>% 
  column_to_rownames(var = 'comp')
sig_pirs_cast <- sig_pirs_cast[ordering(rownames(sig_pirs_cast),
                                        c(r_order_vector,
                                          'Gam.Male_Asex.Mixed',
                                          'Gam.Male_Liv.Meroz')),
                               sig_pirs_order]

sig_pirs %>% filter(Geneid %in% 'PBANKA_0317181', grepl(comp, pattern = 'Male'))
sig_pirs %>% filter(Geneid %in% 'PBANKA_0600031', grepl(comp, pattern = 'Meroz'))
```

@@

```{r save_stats_df}
write_xlsx(deseq_stats, 
           'SupplementaryInformation4_Stats_DESEQ_berghei.xlsx')
write.csv(deseq_stats, 
           'SupplementaryInformation4_Stats_DESEQ_berghei.csv')
deseq_stats <- read.csv('SupplementaryInformation4_Stats_DESEQ_berghei.csv',
                        row.names = 1)
```
